Data Recovery and Pulse Position Modulation with a Photon Number Resolving SNSPD

### 2023-10-10 manuscript.tex
overleaf update

\author{Author One,\authormark{1} Author Two,\authormark{2,*} and Author Three\authormark{2,3}}

\address{\authormark{1}Peer Review, Publications Department, Optica Publishing Group, 2010 Massachusetts Avenue NW, Washington, DC 20036, USA\\
\authormark{2}Publications Department, Optica Publishing Group, 2010 Massachusetts Avenue NW, Washington, DC 20036, USA\\
\authormark{3}Currently with the Department of Electronic Journals, Optica Publishing Group, 2010 Massachusetts Avenue NW, Washington, DC 20036, USA}

\email{\authormark{*}opex@optica.org} %% email address is required; see note below about the corresponding author designation

@@

\hypertarget{fig:intro}{%
\begin{figure}
\centering
\includegraphics[width=1\textwidth]{./figs_03/fig_intro_2_light.pdf}
\caption[{PPM modulation and experiment setup}]{\textbf{PPM modulation and experiment setup} a) Diagram of the expiremental setup. WG: wave generator, CD: clock divider board, AWG: Arbitrary Waveform Generator, MLL: Mode Locked Laser (Pritel UAC), IM: Intensity Modulator, BC: Bias Controller, FSC: Free Space Coupling System, DCA: DC Coupled Cryo-amp b) How bits are transmitted in M=16 PPM modulation. An optical pulse is transmitted with a clock-referenced integer delay which encodes 4 bits of data. c) XXXXXXXX}
\label{fig:intro}
\end{figure}
}

>>>>

\author{Andrew Mueller\authormark{1, 2, *}, Boris Korzh\authormark{2}, Emma Wollman\authormark{2}, Andrew D. Beyer\authormark{2}, Matthew D. Shaw\authormark{2}, and Maria Spiropulu\authormark{3}}

\address{\authormark{1}Applied Physics, California Institute of Technology, 1200 E California Blvd., Pasadena, CA, 91125, USA \\
\authormark{2}Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Dr., Pasadena, CA, 91109, USA \\
\authormark{3}Division of Physics, Mathematics and Astronomy, California Institute of Technology, 1200 E California Blvd., Pasadena, CA 91125, USA }

\email{\authormark{*}andrewstermueller@gmail.com} %% email address is required; see note below about the corresponding author designation

@@

\hypertarget{fig:intro}{%
\begin{figure}
\centering
\includegraphics[width=1\textwidth]{./figs_03/fig_intro_2_light.pdf}
\caption[{PPM modulation and experiment setup}]{\textbf{PPM modulation and experiment setup} a) Diagram of the expiremental setup. WG: wave generator, CD: clock divider board, AWG: Arbitrary Waveform Generator, MLL: Mode Locked Laser (Pritel UAC), IM: Intensity Modulator, BC: Bias Controller, FSC: Free Space Coupling System, DCA: DC Coupled Cryo-amp b) How bits are transmitted in M=16 PPM modulation. An optical pulse is transmitted with a clock-referenced integer delay which encodes 4 bits of data. c) \textbf{\hl{XXXXXXXX}}}
\label{fig:intro}
\end{figure}
}
